---
title: "Group 3 — Bodies and talk"
subtitle: "Studio wall"
author: "Group names here"
format:
  html:
    toc: true
    toc-depth: 2
---

# Spine

> How do bodies measure, how do people talk about mind and school, and how long do countries live?




# Panel A — body / measure

*height_cm, weight_kg, waist_cm are Quant. sex is Qual.*

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

-We have 6 quantitative variables in our data -  age,weight_kg,height_cm,wasit_cm,hip_cm,chest_cm
and only 1 qualitative varaible - sex 

``` r
# glimpse() / inspect() / skim()
```

```{r}
#| label: setup 

library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
```

```{r}
myPanelAData <- read_csv(file="data/panel-A.csv")
```

```{r}
glimpse(myPanelAData)
```

```{r}
inspect(myPanelAData)
```

```{r}
skim(myPanelAData)
```



### 2. Ask

One question *this* table can answer. One it cannot. Write both.

Who is heavier between men and women ?
what is the proportion of men and women ?
How does waist size vary for men and women?
How does hip size vary for men and women?
How does chest size vary for men and women?
Which sex has a larger variation in their age ranges ?
Who is taller between men and women ?
What are the age ranges in the dataset ?
What is the variation in chest size in the given dataset?
What is the variation in waist size in the given dataset ?
What is the variation in hip size in the given dataset ?
What is the variation in height in the given dataset ?
What is the variation in weight in the given dataset ?

### 3. Choose a mark

Geom, map mark, or (later) test that matches the pair type. Name it before you code.

Who is heavier between men and women ?
-histogram

what is the proportion of men and women ?
-bar graph

How does waist size vary for men and women?
-histogram

How does hip size vary for men and women?
-density

How does chest size vary for men and women
-density

Which sex has a larger variation in their age ranges ?
- bar
 
Who is taller between men and women ?
-histogram

What are the age ranges in the dataset ?
-bar

What is the variation in chest size in the given dataset?
-density 

What is the variation in waist size in the given dataset ?
-density 

What is the variation in hip size in the given dataset ?
-density 

What is the variation in height in the given dataset ?
-density 

What is the variation in weight in the given dataset ?
-density 




### 4. Predict

We predict the graph to depict the chest size and hip size of women to be more than men.
Referring to the stereotypical anatomy , we predict the variation in chest size and hip size  of women to be more than men. 

### 5. Make




1)Who is heavier between men and women  ? `
```{r}
myPanelAData |> gf_histogram(~weight_kg,fill =~sex,bins = 50)

```
2)what is the proportion of men and women ?
```{r}

myPanelAData |> gf_bar(~sex,fill=~sex)

```

3)How does  waist size vary for men and women?
```{r}

myPanelAData |> gf_histogram(~waist_cm,fill=~sex)

```



4)How does hip size vary for men and women?
```{r}

myPanelAData |> gf_density(~hip_cm,fill=~sex)

```

5)How does chest size vary for men and women
```{r}

myPanelAData |> gf_density(~chest_cm,fill=~sex)

```

6)Who is older in the given dataset?
```{r}
myPanelAData |> gf_bar(~ age, fill = ~ sex)
```

7)Who is taller between men and women ? -histogram
```{r}
myPanelAData |> gf_histogram(~height_cm,fill =~sex,bins = 50)
```
8)What are the age ranges in the dataset ?

```{r}
myPanelAData |> gf_bar(~age)
```

9)What is the variation in chest size in the given dataset
```{r}
myPanelAData |> gf_density(~chest_cm)
```
10)What is the variation in waist size in the given dataset
```{r}
myPanelAData |> gf_density(~waist_cm)
```

11)What is the variation in hip size in the given dataset 
```{r}
myPanelAData |> gf_density(~hip_cm)
```

12)What is the variation in height in the given dataset
```{r}
myPanelAData |> gf_density(~height_cm)
```

13)What is the variation in weight in the given dataset
```{r}
myPanelAData |> gf_density(~weight_kg)
```





### 6. Say


We all found the density graph comparing chest sizes of men and women interesting  because according to the graph, men have a bigger chest size than women which is quite unexpected. Men also have larger variation in the sizes while women have more difference in density for different sizes this is surprising because according to the bar graph comparing the count of men and women , women are more in quantity.

We also found the density graph comparing hip size of men and women surprising because it is contrasting the general belief that women have wider hips. 

### 7. Limit

What this panel cannot do. Which kit table we refused to abuse.
```{r}
myPanelAData |> group_by(sex) |> summarise(mean_chest_cm=mean(chest_cm,na.rm=T))
```
```{r}
mosaic::t_test(chest_cm ~ sex, data= myPanelAData)
```



# Panel B — category / talk

*degree × grass is Qual + Qual. mntlhlth is Quant — it belongs in a histogram or a grouped violin, not a mosaic.*

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

The quantitative variables in  the dataset are -hours of relaxation(hrsrelax), hours of labour (hrsl) and mental health(mntlhlth) {3}
The qualitative variables in  the dataset are-degree, marijuana(grass) {2}
``` r
# glimpse() / inspect() / skim()
```
```{r}
myPanelBData <- read_csv(file="data/panel-B.csv")
```
 
```{r}
glimpse(myPanelBData)
```
```{r}
skim(myPanelBData)
```
 

 
### 2. Ask
 
A question the graph can answer -
Does the education of a person affect their opinion on whether marijuana should be legal or not ?

A question the graph cannot answer -



### 3. Choose a mark

Does the education of a person affect their opinion on whether marijuana should be legal or not ?
-Mosaic graph 

### 4. Predict

we predict that a person pursuing a higher education degree would want marijuana to be legal, to regulate stress levels and mental health.

### 5. Make


modifying 

```{r}
myPanelBData_mod <- myPanelBData |> drop_na(grass)
```
```{r}
dim(myPanelBData_mod)
```
```{r}
vcd::structable(degree~grass, data = myPanelBData)
```
```{r}
vcd::structable(degree~grass, data=myPanelBData) |>
  vcd::mosaic(labeling_args = list(rot_labels = c(top = 45)),
              margins = c(top = 6))
```





### 6. Say

looking at the graph, the ratio of people who think marijuana should be legal and not legal appears to be similar, in each individual degree. 
saying that, it is surprising information to see that the percentage of high schoolers who want marijuana to be legal is way larger than any other degrees.But this could also be because the number of high schoolers in this dataset is much more. 

### 7. Limit


# Panel C — place

*lifeExp is the honest fill. pop is a count — symbol map, not choropleth.*

Geometry is not in the CSV. Join in R, then use the same seven headings.

``` r
# library(sf) # library(rnaturalearth) # world <- ne_countries(scale = "medium", returnclass = "sf") # # join on country name; list the unmatched labels
```

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

``` r
# glimpse() / inspect() / skim()
```

### 2. Ask

One question *this* table can answer. One it cannot. Write both.

### 3. Choose a mark

Geom, map mark, or (later) test that matches the pair type. Name it before you code.

### 4. Predict

What do we think we will see? One sentence, before Run.

### 5. Make

Human brick first. Optional: one AI prompt, pasted below, only for what section 3 named.

``` r
# human chunk  # ## Prompt we actually used # ai_draft # ours
```

### 6. Say

Caption + one sentence we will stand behind. Title is a sentence, not a column name.

### 7. Limit

What this panel cannot do. Which kit table we refused to abuse.

# Conclusion

What the spine looks like after three panels.

- The question we will defend in ninety seconds
- What we will **not** claim
- Which lines were human, which were machine
- Limits: sample, missingness, the test we did not run
- Gift for the steal-this strip (palette, annotation, join trick)
